### 2021-08-04 paper/paper.tex
do not introduce DG twice
reformulate CI stuff

  \item High-order matrix-free discontinuous Galerkin (DG) methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

Julia itself and most packages are developed on GitHub. The community provides
many tools to use corresponding CI setups to prepare and publish
documentation\footnote{\url{https://github.com/JuliaDocs/Documenter.jl}},
and related tasks. This setup also encourages other good software development
practices that we use in \trixi, such as mandatory code review before pull requests
are merged.

>>>>

  \item High-order matrix-free discontinuous Galerkin methods
  \begin{itemize}
    \item Kinetic energy preserving and entropy-stable methods
    \item Entropy-stable shock-capturing
    \item Positivity-preserving limiting
  \end{itemize}

@@

Julia itself and most packages are developed on GitHub. The community provides
many tools one can use to run corresponding CI setups, prepare and publish
documentation\footnote{\url{https://github.com/JuliaDocs/Documenter.jl}},
and other related tasks. This setup also encourages other good software development
practices that we use in \trixi, such as mandatory code review before pull requests
are merged.
